Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-17 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
updated some language in the markdown file.

# knitr options
knitr::opts_chunk$set(fig.width=12, fig.height=10, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

@@

Most of the heavy smoke days were in the south-west part of Oregon. I've added county names to map but some text aren't well placed. I should probably use centroid, but then I'll have to import a shapefile to do this. I'll fix this later; I plan to add in fire locations.

@@

```{r same day association graph}
class <- as_tibble(c(rep("Respiratory", times = 6), 
  rep("Cardiovascular", times = 6))) %>% 
  rename(class = value)
# add a class indicator to table
sameday_results_w_class <- sameday_results %>% bind_cols(class)
  sameday_results_w_class

@@

# add a class indicator to table
cumulative_results_w_class <- cumulative_results %>% bind_cols(class)
  cumulative_results_w_class

>>>>

# knitr options
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

@@

Most of the heavy smoke days were in the south-west part of Oregon. Triangles are fires; had them in the legend, but the legend looked weird so I took them out.

@@

```{r same day association graph}
class <- as_tibble(c(rep("Respiratory", times = 6), 
  rep("Cardiovascular", times = 6))) %>% 
  rename(class = value)
# add a class indicator to table
sameday_results_w_class <- sameday_results %>% bind_cols(class)

@@

# add a class indicator to table
cumulative_results_w_class <- cumulative_results %>% bind_cols(class)
